Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
cav

In this study, we focus on Cyber-Physical Systems with continuous 
dynamical plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
\end{align}
%

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Counterexample Guided Abstractly Refined Inductive Synthesis for LTI Cyberphysical Systems}\label{sec:CEGARIS}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Verification of a Conrollable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

>>>>

We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
\end{align}
where $A$ and $B$ are matrices that fully specify the continuous plant. 
Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
%
\begin{align}
\label{eq:plant}
x_{k+1}&= A_d x_k+ B_d u_k. 
\end{align}
%
The

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Controllers for LTI Systems} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%-------------------------------
\section{Extensions}
\label{sec:extensions}
%-------------------------------

%-------------------------------
\subsection{LTI systems with output} 
\label{ssec:LTI}
%-------------------------------

LTI models in the form: 
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
\end{align}
%
